Light Transport Techniques for Tensor Field Visualization

### 2019-08-09 beamer2thesis/dummy.tex
update

\frame{
\frametitle{{Introduction - Tensor Fields}}
\begin{columns}
\begin{column}{.5\textwidth}
\begin{itemize}
	\item tensor-valued function: $\mathop{t_{ij}\mathbf{(x)}\colon} \mathbf{x}\mapsto t$, with $\mathbf{x}\in\mathcal{R}^n$: location vector
	\bigskip
	\item tensor fields can be visualized by:
	\begin{itemize}
		\item a) glyphs
		\item b) tensor field lines (TFLs)\\ $\Rightarrow$ streamlines for eigenvector fields
		\item c) scalar measures:\\ anisotropy index, tensor magnitude
	\end{itemize}
	\bigskip
	\item examples: stress tensor

\end{itemize}
\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[t]
\centering
\caption*{\textit{Random tensor field}}\bigskip
\begin{minipage}{0.49\textwidth}
\centering
\includegraphics[height=\textwidth]{random-global.png} {\scriptsize a) Glyphs}
\end{minipage}
\begin{minipage}{0.49\textwidth}
\centering
\includegraphics[height=\textwidth]{random-global-TFL.png} {\scriptsize b) Tensor field lines}
\end{minipage}
\end{figure}

>>>>

\frame{
\frametitle{{Light Transport Gradient (LTG) - Isotropic field}}
\begin{columns}
\begin{column}{.5\textwidth}
\begin{small}
\begin{itemize}
	\item Isotropic test field reveals offset response for the approach
	\bigskip
	\item natural shift against the inital light source (slice) direction (left)\\
%	$\Rightarrow$ initial light source configurations located close and pointing towards borders, are biased for low LTG (FTLE) responses
\end{itemize}
\end{small}
\end{column}
\begin{column}{.5\textwidth}
\begin{figure}[t]
\caption*{\textit{Isotropic test field}}\bigskip
\begin{minipage}{.49\textwidth}
\includegraphics[height=\textwidth]{isotropic2.png} \caption*{a)~Glyphs}
\end{minipage}
\begin{minipage}{.49\textwidth}
\includegraphics[height=\textwidth]{iso_ftle.png} \caption*{b)~LTG($0^\circ$)}
\end{minipage}

\end{figure}
